A Bias-Variance Decomposition of Information Transfer in Multi-Task Learning

### 2020-08-19 arxiv/setup.tex
pf
edits

\medskip
\noindent\textbf{Hard parameter sharing.}
We study multi-task learning models that use hard parameter sharing, which is the most commonly used architecture in practice \cite{R17}.
Specifically, we consider a two-layer neural network with a shared layer $B\in\real^{p\times r}$ for all tasks and $t$ output layers $W_1, \dots, W_t$ for every task from $1$ to $t$, where each output layer is a $r$-dimensional vector.
The width of $B$, denoted by $r$, plays an important role in regularization.
As observed in Proposition 1 of \cite{WZR20}, if $r \ge t$, there is no regularization effect.
Hence, we assume that $r < t$ in our study.
%For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
We study the following procedure inspired by how hard parameter sharing models are trained in practice.
\begin{enumerate}
	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
	The size of each set is described below.
	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a closed form equation for $\hat{B}$ that depends on $W_1,\dots, W_k$.
		{\begin{align}\label{eq_mtl}
			f(B; W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k^{\text{tr}} B W_k - Y_k^{\text{tr}}}^2.
		\end{align}}
	\item Tune the output layers $W_i$: set $B = \hat{B}$ and minimize the validation loss over $W_1,\dots, W_k$.
		{\begin{align}\label{eq_mtl_eval}
			g(W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k^{\text{val}} \hat{B} W_k - Y_k^{\text{val}}}^2.
		\end{align}}
\end{enumerate}
Let $\hat{\beta}_t^{\MTL}$ denote the multi-task learning estimator obtained from the procedure above.
By contrast, let $\hat{\beta}_t^{\STL} = (X_t^{\top}X_t)^{-1}X_t^{\top}{Y_t}$ denote the single-task learning estimator. % denoted by $L(\hat{\beta}_t^{\STL})$.
%where $B\in\real^{p\times r}$ and $W_k\in\real^r$ for every $1\le k\le t$.
%Following , we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.
In general, the objective $f(\cdot)$ is non-convex in $B$ and the $W_k$'s.
Therefore, we first minimize $B$ in equation \eqref{eq_mtl} and then minimize $W_k$ given $B$ in equation \eqref{eq_mtl_eval}.
For our purpose, a validation set that is much larger than the number of output layer parameters $r\cdot t$ suffices (e.g. $\rho_i \cdot p^{0.5}$).
%The size of the training set is then $\rho_i (p - p^{0.99})$.
The advantage of tuning the output layers on the validation set is to reduce the effect of noise from $\hat{B}$.
%For more details, we refer the reader to Appendix \ref{app_proof_sec3}.

>>>>

\medskip
\noindent\textbf{Hard parameter sharing.}
We study multi-task learning models that use hard parameter sharing, which is the most commonly used architecture in practice \cite{R17}.
Specifically, we consider a two-layer neural network with a shared layer $B\in\real^{p\times r}$ for all tasks and $t$ output layers $W_1, \dots, W_t$ for every task from $1$ to $t$, where each output layer is a $r$-dimensional vector.
The width of $B$, denoted by $r$, plays an important role in regularization.
As observed in Proposition 1 of \cite{WZR20}, if $r \ge t$, there is no regularization effect.
Hence, we assume that $r < t$ in our study.
%For example, when there are only two tasks, $r = 1$ and $B$ reduces to a vector whereas $W_1, W_2$ become scalars.
We study the following procedure inspired by how hard parameter sharing models are trained in practice.
\begin{enumerate}
%	\item Separate each dataset $(X_i, Y_i)$ randomly into a training set $(X_i^{tr}, Y_i^{tr})$ and a validation set $(X_i^{val}, Y_i^{val})$.
%	The size of each set is described below.
	\item Learn the shared layer $B$: minimize the training loss over $B$ and $W_1, \dots, W_t$, leading to a local minimum of $B$ that depends on $W_1, \dots, W_t$, denoted by $\hat{B} = \hat{B}(W_1, \dots, W_t)$.
		{\begin{align}\label{eq_mtl}
			f(B; W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k B W_k - Y_k}^2.
		\end{align}}
	\item Learn the output layers $W_1, W_2, \dots, W_t$: set $B = \hat{B}$ and minimize the training loss over $W_1, W_2, \dots, W_t$.
		{\begin{align}\label{eq_mtl_eval}
			g(W_1, \dots, W_t) = \sum_{k=1}^t \norm{X_k \hat{B} W_k - Y_k}^2.
		\end{align}}
\end{enumerate}
Let $\hat{\beta}_t^{\MTL}$ denote the multi-task learning estimator obtained from the procedure above.
By contrast, let $\hat{\beta}_t^{\STL} = (X_t^{\top}X_t)^{-1}X_t^{\top}{Y_t}$ denote the single-task learning estimator. % denoted by $L(\hat{\beta}_t^{\STL})$.
%where $B\in\real^{p\times r}$ and $W_k\in\real^r$ for every $1\le k\le t$.
%Following , we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ being the single-task optimum.
In general, the objective $f(\cdot)$ is non-convex in $B$ and the $W_k$'s.
Therefore, we first minimize $B$ in equation \eqref{eq_mtl} and then minimize $W_k$ given $B$ in equation \eqref{eq_mtl_eval}.
%For our purpose, a validation set that is much larger than the number of output layer parameters $r\cdot t$ suffices (e.g. $\rho_i \cdot p^{0.5}$).
%The size of the training set is then $\rho_i (p - p^{0.99})$.
%The advantage of tuning the output layers on the validation set is to reduce the effect of noise from $\hat{B}$.
%For more details, we refer the reader to Appendix \ref{app_proof_sec3}.
